Forcasting US Elections using Polls-of-Polls

### 2024-10-22 paper/paper.qmd
Added a subtitle.

---
title: Forcasting US Elections using Polls-of-Polls
subtitle: "My subtitle if needed"
author: 
  - Shamayla Durrin
  - Denise Chang 
  - Krishna Kumar
thanks: "Code and data are available at: [https://github.com/krishnak30/US_elections](https://github.com/krishnak30/US_elections)."
date: today
date-format: long
abstract: "This paper uses a polls of polls approach to predict voter support for Kamala Harris in the 2024 U.S. election, aggregating multiple polls to reduce individual bias and improve accuracy. Through a regression model incorporating factors such as pollster, sample size, state, and recency, we predict her overall support to be 47.78%, just below the 50% threshold. Our analysis highlights the importance of poll quality and recency in understanding trends in public opinion. These findings are significant as they provide a more reliable estimate of electoral outcomes, helping to inform political strategies and public discourse."
format: html
number-sections: true
bibliography: references.bib
---

@@

### Political Leanings of Different State

[@fig-mapinterac] provides a state-level representation of Kamala Harris's average support across the U.S., with the darker blue shades indicating states where her support is higher, and the redder tones showing where her support is lower. Gray areas represent states where we have no polling data available.

The gradient highlights notable geographic trends. Harris has the strongest support in states like Vermont, Massachusetts, and New York, while states like Utah and West Virginia show considerably lower levels of support. A distinct pattern emerges in the West, where coastal states like California favor Harris more strongly, contrasting with inland states like Wyoming and Utah.

This reveals that political leanings differ greatly by state, and this regional variation should be controlled for in any regression model analyzing poll data. The map serves as a useful tool for visualizing regional variations in voter support for Kamala Harris as reflected in the available polling data.

```{r}
#| warning: false
#| message: false
#| echo: false
# Filter out non-continental states (Hawaii and Alaska)
us_states_filtered <- mapping_data %>% 
  filter(!NAME %in% c("Alaska", "Hawaii"))

# Ensure correct merge between map data and Kamala's support data
map_data_full <- left_join(us_states_filtered, mean_support_data, by = c("NAME" = "state"))

# Create centroids for state labels
state_centroids <- st_centroid(us_states_filtered)

# Plot using geom_sf() for sf objects
p <- ggplot(map_data_full) +
  geom_sf(aes(fill = mean_support, text = paste("State:", str_to_title(NAME), "<br>Average Support:", round(mean_support, 2))), color = "white") +  # Capitalize state names
  scale_fill_distiller(palette = "RdBu", direction = 1, na.value = "gray", name = "Kamala's Support") +  # Reverse RdBu color gradient
  geom_text(data = state_centroids, aes(geometry = geometry, label = STUSPS), stat = "sf_coordinates", size = 2) +  # State labels
  labs(title = "Support for Kamala Harris by State", 
       caption = "States with no polling data are shown in gray") +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5),
    panel.grid = element_blank(),  # Remove grid lines
    axis.title = element_blank(),  # No axis titles for maps
    axis.text = element_blank(),   # No axis labels
    axis.ticks = element_blank()   # No axis ticks
  )

# Turn ggplot to plotly for interactivity, add hover template for better control over display
ggplotly(p, tooltip = "text")

@@

## Overview
Emerson College Polling, known for its extensive online polling methods, conducted a survey from October 14 to 16, 2024, targeting 1,000 likely voters. The poll measured voter preferences between Kamala Harris and Donald Trump, revealing a near tie with Harris at 50% and Trump at 49%.

## Population, Frame, and Sample
The target population is likely voters in the U.S. elections. These voters are determined by the voters' likeliness to vote in the upcoming elections and the voter's voting history. Both of these factors are self-reported.

@@

## Sample Recruitment and Approach
Emerson College used a mixed-mode sampling approach for its polling. Specifically, three primary modes were used to collect data for its October 14-16, 2024 poll:

@@

## Advantages and Trade-offs in Mixed-Mode Sampling
The multi-mode sampling approach used in this poll has several advantages:

@@

## Non-response Handling
Emerson addresses non-response using a weighting system. The data is adjusted based on key demographic variables like age, gender, race, education, and party affiliation, making the sample more representative of the electorate. Weights are applied to compensate for under- or over-represented groups, ensuring balanced results.

## Questionnaire Design
The Emerson survey features a straightforward, efficient design focused on key issues and voter preferences. Strengths of the questionnaire include:

@@

## Conclusion
Emerson College Polling's mixed-mode methodology is effective in balancing cost with broad demographic reach. Its weighting techniques contribute to reliable and accurate results despite non-responses. While the use of multiple survey modes increases population representation, possible biases—such as lack of nuance and mode effects need to be taken into consideration when interpreting results.

@@

## Overview
This methodology outlines an election forecasting plan with a budget of $100,000. Heavily inspired by TIPP Insights and Emerson College's hybrid approaches, the survey methodology balances cost-efficiency and data accuracy by using different modes of data collection and wide demographic reach.

@@

## Sampling Approach
This idealized methodology uses a multi-mode hybrid sampling approach. This allows the use of both probability-based and non-probability-based methods:

@@

## Recruitment Strategy
By using Aristotle’s voter lists and CINT's platform as a sampling frame, the sample consists of likely voters based on registration status and past voting behavior. Quota sampling would be used to match the demographic profile of the U.S. electorate. This ensures that respondents in the sample reflect key demographic variables such as age, gender, race, and education level.

@@

## Conclusion
By combining TIPP’s live phone/IVR hybrid and Emerson College’s mixed-mode survey methods, this idealized methodology captures diverse voter demographics. It uses both probability-based and non-probability-based sampling methods to forecast the 2024 U.S. Presidential Election.

>>>>

---
title: Forcasting US Elections using Polls-of-Polls
subtitle: Using a Linear Regression Model to Adjust Pollster Biases and Predict Kamala Harris' Vote Percentage at 47.78%
author: 
  - Shamayla Durrin
  - Denise Chang 
  - Krishna Kumar
thanks: "Code and data are available at: [https://github.com/krishnak30/US_elections](https://github.com/krishnak30/US_elections)."
date: today
date-format: long
abstract: "This paper uses a polls of polls approach to predict voter support for Kamala Harris in the 2024 U.S. election, aggregating multiple polls to reduce individual bias and improve accuracy. Through a regression model incorporating factors such as pollster, sample size, state, and recency, we predict her overall support to be 47.78%, just below the 50% threshold. Our analysis highlights the importance of poll quality and recency in understanding trends in public opinion. These findings are significant as they provide a more reliable estimate of electoral outcomes, helping to inform political strategies and public discourse."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@@

## Overview

Emerson College Polling, known for its extensive online polling methods, conducted a survey from October 14 to 16, 2024, targeting 1,000 likely voters. The poll measured voter preferences between Kamala Harris and Donald Trump, revealing a near tie with Harris at 50% and Trump at 49%.

## Population, Frame, and Sample

The target population is likely voters in the U.S. elections. These voters are determined by the voters' likeliness to vote in the upcoming elections and the voter's voting history. Both of these factors are self-reported.

@@

## Sample Recruitment and Approach

Emerson College used a mixed-mode sampling approach for its polling. Specifically, three primary modes were used to collect data for its October 14-16, 2024 poll:

@@

## Advantages and Trade-offs in Mixed-Mode Sampling

The multi-mode sampling approach used in this poll has several advantages:

@@

## Non-response Handling

Emerson addresses non-response using a weighting system. The data is adjusted based on key demographic variables like age, gender, race, education, and party affiliation, making the sample more representative of the electorate. Weights are applied to compensate for under- or over-represented groups, ensuring balanced results.

## Questionnaire Design

The Emerson survey features a straightforward, efficient design focused on key issues and voter preferences. Strengths of the questionnaire include:

@@

## Conclusion

Emerson College Polling's mixed-mode methodology is effective in balancing cost with broad demographic reach. Its weighting techniques contribute to reliable and accurate results despite non-responses. While the use of multiple survey modes increases population representation, possible biases—such as lack of nuance and mode effects need to be taken into consideration when interpreting results.

@@

## Overview

This methodology outlines an election forecasting plan with a budget of \$100,000. Heavily inspired by TIPP Insights and Emerson College's hybrid approaches, the survey methodology balances cost-efficiency and data accuracy by using different modes of data collection and wide demographic reach.

@@

## Sampling Approach

This idealized methodology uses a multi-mode hybrid sampling approach. This allows the use of both probability-based and non-probability-based methods:

@@

## Recruitment Strategy

By using Aristotle’s voter lists and CINT's platform as a sampling frame, the sample consists of likely voters based on registration status and past voting behavior. Quota sampling would be used to match the demographic profile of the U.S. electorate. This ensures that respondents in the sample reflect key demographic variables such as age, gender, race, and education level.

@@

## Conclusion

By combining TIPP’s live phone/IVR hybrid and Emerson College’s mixed-mode survey methods, this idealized methodology captures diverse voter demographics. It uses both probability-based and non-probability-based sampling methods to forecast the 2024 U.S. Presidential Election.
